Questions\vspace{-.1cm}

### 2020-07-21 NetworkSlicing/report3.tex
add to system model
add

\title{Joint Power Allocation and Network Slicing in an Open RAN System \vspace{-.1cm}
}
%
%\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%salar.nouri@ut.ac.ir}
%}
  \author{
    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb}
    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
    Email: \{mojdeh.karbalaee\}@ut.ac.ir,
    \vspace{-.2cm}
  }
  }

@@

Game theory is generally defined as the mathematics of conflicts and are being utilized in various fields like economy, psychology, AI, sociology etc. In Game theory w.r.t RL, the policy is the strategy, mapping all possible state of actions, in respect to one of the players of the game.
The types of games in Multi-Agent RL (MARL) are:
● Static Games : players are independent and make simultaneous decision
● Stage Games : the rules depend on specific stages
● Repeated Games : when a game is played in sequence
\begin{figure}%[H]
  \centering
    \includegraphics[width=\linewidth]{rlfig}
  \caption{Multiple agents acting in the same environment \cite{rl1}}
  \label{fig:qos}
\end{figure}
%%
An extension of the single agent Markov decision process (MDP) to the multi-agent
case can be defined by Markov Games. In a Markov Game, joint actions are the
result of multiple agents choosing an action independently.
While in normal form games the challenges for reinforcement learners originate
mainly from the interactions between the agents, in Markov games they face the
additional challenge of an environment with state transitions. This means that the
agents typically need to combine coordination methods or equilibrium solvers used
in repeated games with MDP approaches from single-agent RL.
\item  \textbf{Find best delay formula which is the nearest to reality (M/M/1 M/D/1 M/G/1)}
\begin{figure}%[H]
  \centering
    \includegraphics[width=\linewidth]{delay1}
  \caption{ Latency contribution in E2E delay of a packet transmission \cite{delay}}
  \label{fig:delay}
\end{figure}
In the LTE system, the latency can be divided into two
major parts: (1) user plane (U-plane) latency and (2) control
plane (C-plane) latency. The U-plane latency is measured by 
one directional transmit time of a packet to become available
in the IP layer between evolved UMTS terrestrial radio access
network (E-UTRAN) edge/UE and UE/E-UTRAN node.
On the other hand, C-plane latency can be defined as the
transition time of a UE to switch from idle state to active
state. At the idle state, an UE is not connected with radio
resource control (RRC). After the RRC connection is being
setup, the UE switches from idle state into connected state
and then enters into active state after moving into dedicated
mode. Since the application performance is dependent mainly
on the U-plane latency, U-plane is the main focus of interest
for low latency communication.
In the U-plane, the delay of a packet transmission in a
cellular network can be contributed by the RAN, backhaul,
core network, and data center/Internet.
\begin{equation}
T = T_{Radio} + T_{Backhaul} + T_{Core} + T_{Transport}
\end{equation}
\begin{itemize}
\item TRadio

@@

 is the delay to data communication between
the core network and Internet/cloud. Generally, distance
between the core network and the server, bandwidth, and
communication protocol affect this latency
\end{itemize}
\begin{equation}
T_{Radio} = t_{Q} + t_{FA} + t_{tx} + t_{bsp} + t_{mpt}
\end{equation}
\begin{itemize}
\item tQ is the queuing delay which depends on the number of
users that will be multiplexed on same resources;
\item tFA is the delay due to frame alignment which depends on
the frame structure and duplexing modes (i.e., frequency
division duplexing (FDD) and time division duplexing
(TDD));
\item ttx is the time for transmission processing, and payload
transmission which uses at least one TTI depending on
radio channel condition, payload size, available resources,
transmission errors and retransmission;
\item tbsp is the processing delay at the base station;
\item  tmpt is the processing delay of user terminal. Both
the base station and user terminal delay depend on the
capabilities of base station and user terminal (i.e., UE),
respectively.
\end{itemize}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda$.
It is assumed that there are load balancers in each layer for each slice to divide the incoming traffic to VNFs equally \cite{frdl,luong2018novel,luong2018novel1}.
Suppose the baseband processing of each VNF is depicted as an M/M/1 processing queue.
Each packet is processed by one of the VNFs of a slice. So, the mean delay of  slice, modeled as M/M/1 queue, is formulated as follow, respectively
\begin{equation}
d = \frac{1}{\mu - \alpha/{M}}
\end{equation}
where $1/\mu$ is the mean service time.
Besides, $\alpha$ is the  arrival rate which is divided
by load balancer before arriving to the VNFs. The  arrival rate of each VNF in each layer of the slice $s$ is $\alpha/{M}$.
In addition, $d_{tr}$ is the transmission delay on the  wireless link. The arrival data rate of wireless link
 is equal to the arrival data rate of load balancers for each slice \cite{frdl}.
Moreover, it is assumed that the service time of transmission queue has
 an exponential distribution with mean $1/(R_{{tot}})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. Therefore,
the mean delay of the transmission layer is
\begin{equation}
 d_{tr} = \frac{1}{R_{{tot}} - \alpha};
\end{equation}
where, $R_{{tot}}$ is the total achievable rate of each slice that is mapped to specific service.
Mean delay of each slice is obtained as below.
\begin{equation}
D_{s} = d+ d_{{tr}}
\end{equation}
\begin{figure}%[H]
  \centering
    \includegraphics[width=\linewidth]{delay}
  \caption{ delay of a packet \cite{frdl}}
  \label{fig:delay}
\end{figure}
\item \textbf{Assume a system model for the paper}

@@

Each VNF requires
physical resources that contain memory, storage and CPU.
Let the required resources for VNF $f$ in slice $s$ is represented by a tuple as
\begin{equation}
\bar{\Omega}_{s}^f = \{\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f \},
\end{equation}
where $\bar{\Omega}_{s}^f\in \mathbb{C}^{3}$ and $\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f$ indicate the amount of required memory, storage, and CPU, respectively.
Moreover, the total amount of required memory, storage and CPU of all VNFs of a slice is defined as
\begin{equation}
\textstyle \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{M_s}\bar{\Omega}_{\mathfrak{z},s}^f \;\; \mathfrak{z} \in \{M, S, C\}.
\end{equation}
Also, there are $D_c$ data centers (DC), serving the VNFs. Each DC contains several servers that supply VNF requirements.
The amount of memory, storage and CPU is denoted by $\tau_{M_{j}}, \tau_{S_{j}}$and $\tau_{C_{j}} $ for the $j^{th}$ DC, respectively
\begin{equation*}
\tau_j = \{\tau_{M_{j}}, \tau_{S_{j}}, \tau_{C_{j}} \},
\end{equation*}
In this system model, the assignment of physical DC resources to VNFs is considered. Let $y_{s,d}$ be a binary variable indicating whether the $d^{th}$ DC is connected to the VNFs of $s^{th}$ slice or not.
Assume the power consumption of baseband processing at each DC $d$ that is connected to VNFs of a slice $s$ is depicted as
$\phi_{s,d}$. So the total power of the system for all active DCs that are connected to slices can be represented as
\begin{equation*}
\textstyle \phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi_{s,d}.
\end{equation*}
Also, a cost function for the placement of VNFs into DCs is defined as
\begin{equation}\label{eqpsi}
\textstyle  \psi_{tot} = \phi_{tot} - \nu \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s}
\end{equation}
where, $\nu$ is a design variable to value between the first term of \eqref{eqpsi} which is the total power consumption of physical resources and the second term that is shown the amount of admitted slices to have physical resources.
\begin{subequations}
\begin{alignat}{4}
\min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})\\
\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s, \\
 &\textstyle  \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d,, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
\end{alignat}
\end{subequations}
\end{enumerate}

\bibliographystyle{IEEEtran}
\bibliography{references}
\end{document}

>>>>

\title{Questions\vspace{-.1cm}
}
%
%\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%salar.nouri@ut.ac.ir}
%}
  \author{
    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb}
    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
    Email: \{mojdeh.karbalaee\}@ut.ac.ir,
    \vspace{-.2cm}
  }
  }

@@

Game theory is generally defined as the mathematics of conflicts and are being utilized in various fields like economy, psychology, AI, sociology etc. In Game theory w.r.t RL, the policy is the strategy, mapping all possible state of actions, in respect to one of the players of the game.
The types of games in Multi-Agent RL (MARL) are:
Static Games : players are independent and make simultaneous decision

Stage Games : the rules depend on specific stages

Repeated Games : when a game is played in sequence
\begin{figure}%[H]
  \centering
    \includegraphics[width=\linewidth]{rlfig}
  \caption{Multiple agents acting in the same environment \cite{rl1}}
  \label{fig:qos}
\end{figure}
%%
An extension of the single agent Markov decision process (MDP) to the multi-agent
case can be defined by Markov Games. In a Markov Game, joint actions are the
result of multiple agents choosing an action independently.
While in normal form games the challenges for reinforcement learners originate
mainly from the interactions between the agents, in Markov games they face the
additional challenge of an environment with state transitions. This means that the
agents typically need to combine coordination methods or equilibrium solvers used
in repeated games with MDP approaches from single-agent RL.
\item  \textbf{Find best delay formula which is the nearest to reality (M/M/1 M/D/1 M/G/1)}
\begin{figure}%[H]
  \centering
    \includegraphics[width=\linewidth]{delay1}
  \caption{ Latency contribution in E2E delay of a packet transmission \cite{delay}}
  \label{fig:delay}
\end{figure}
In the LTE system, the latency can be divided into two
major parts: (1) user plane (U-plane) latency and (2) control
plane (C-plane) latency. The U-plane latency is measured by 
one directional transmit time of a packet to become available
in the IP layer between evolved UMTS terrestrial radio access
network (E-UTRAN) edge/UE and UE/E-UTRAN node.
On the other hand, C-plane latency can be defined as the
transition time of a UE to switch from idle state to active
state. At the idle state, an UE is not connected with radio
resource control (RRC). After the RRC connection is being
setup, the UE switches from idle state into connected state
and then enters into active state after moving into dedicated
mode. Since the application performance is dependent mainly
on the U-plane latency, U-plane is the main focus of interest
for low latency communication.
In the U-plane, the delay of a packet transmission in a
cellular network can be contributed by the RAN, backhaul,
core network, and data center/Internet.
\begin{equation}
T = T_{Radio} + T_{Backhaul} + T_{Core} + T_{Transport}
\end{equation}
\begin{itemize}
\item TRadio

@@

 is the delay to data communication between
the core network and Internet/cloud. Generally, distance
between the core network and the server, bandwidth, and
communication protocol affect this latency
\end{itemize}
\begin{equation}
T_{Radio} = t_{Q} + t_{FA} + t_{tx} + t_{bsp} + t_{mpt}
\end{equation}
\begin{itemize}
\item tQ is the queuing delay which depends on the number of
users that will be multiplexed on same resources;
\item tFA is the delay due to frame alignment which depends on
the frame structure and duplexing modes (i.e., frequency
division duplexing (FDD) and time division duplexing
(TDD));
\item ttx is the time for transmission processing, and payload
transmission which uses at least one TTI depending on
radio channel condition, payload size, available resources,
transmission errors and retransmission;
\item tbsp is the processing delay at the base station;
\item  tmpt is the processing delay of user terminal. Both
the base station and user terminal delay depend on the
capabilities of base station and user terminal (i.e., UE),
respectively.
\end{itemize}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda$.
It is assumed that there are load balancers in each layer for each slice to divide the incoming traffic to VNFs equally \cite{frdl,luong2018novel,luong2018novel1}.
Suppose the baseband processing of each VNF is depicted as an M/M/1 processing queue.
Each packet is processed by one of the VNFs of a slice. So, the mean delay of  slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follow, respectively
\begin{equation}
\begin{split}
d_{1} &= \frac{1}{\mu_1 - \alpha/{M_{1}}},\\
d_{2} &= \frac{1}{\mu_2 - \alpha/{M_{2}}}.
\end{split}
\end{equation}
where $1/\mu_1$ and $1/\mu_2$ are the mean service time of the first and the second layers respectively.
Besides, $\alpha$ is the  arrival rate which is divided
by load balancer before arriving to the VNFs. The  arrival rate of each VNF in each layer of the slice $s$ is $\alpha/{M_{i}}$ $ i \in \{1,2\}$.
In addition, $d_{tr}$ is the transmission delay on the  wireless link. The arrival data rate of wireless link
 is equal to the arrival data rate of load balancers for each slice \cite{frdl}.
Moreover, it is assumed that the service time of transmission queue for each slice $s$ has
 an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. Therefore,
the mean delay of the transmission layer is
\begin{equation}
 d_{tr} = \frac{1}{R_{{tot}} - \alpha};
\end{equation}
where, $R_{{tot}}$ is the total achievable rate of each slice that is mapped to specific service.
Mean delay of each slice is obtained as below.
\begin{equation}
D_{s} = d_{s_1} + d_{s_2} + d_{{tr}}
\end{equation}
\begin{figure}%[H]
  \centering
    \includegraphics[width=\linewidth]{delay}
  \caption{ delay of a packet \cite{frdl}}
  \label{fig:delay}
\end{figure}
\item \textbf{Assume a system model for the paper}

\textbf{VNF placement after Network Slicing}

@@

Each VNF requires
physical resources that contain memory, storage and CPU.
Let the required resources for VNF $f$ in slice $s$ is represented by a tuple as
\begin{equation}
\bar{\Omega}_{s}^f = \{\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f \},
\end{equation}
where $\bar{\Omega}_{s}^f\in \mathbb{C}^{3}$ and $\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f$ indicate the amount of required memory, storage, and CPU, respectively.
Moreover, the total amount of required memory, storage and CPU of all VNFs of a slice is defined as
\begin{equation}
\textstyle \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{M_s}\bar{\Omega}_{\mathfrak{z},s}^f \;\; \mathfrak{z} \in \{M, S, C\}.
\end{equation}
Also, there are $D_c$ data centers (DC), serving the VNFs. Each DC contains several servers that supply VNF requirements.
The amount of memory, storage and CPU is denoted by $\tau_{M_{j}}, \tau_{S_{j}}$and $\tau_{C_{j}} $ for the $j^{th}$ DC, respectively
\begin{equation*}
\tau_j = \{\tau_{M_{j}}, \tau_{S_{j}}, \tau_{C_{j}} \},
\end{equation*}
In this system model, the assignment of physical DC resources to VNFs is considered. Let $y_{s,d}$ be a binary variable indicating whether the $d^{th}$ DC is connected to the VNFs of $s^{th}$ slice or not.
Assume the power consumption of baseband processing at each DC $d$ that is connected to VNFs of a slice $s$ is depicted as
$\phi_{s,d}$. So the total power of the system for all active DCs that are connected to slices can be represented as
\begin{equation*}
\textstyle \phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi_{s,d}.
\end{equation*}
Also, a cost function for the placement of VNFs into DCs is defined as
\begin{equation}\label{eqpsi}
\textstyle  \psi_{tot} = \phi_{tot} - \nu \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s}
\end{equation}
where, $\nu$ is a design variable to value between the first term of \eqref{eqpsi} which is the total power consumption of physical resources and the second term that is shown the amount of admitted slices to have physical resources.
\begin{subequations}
\begin{alignat}{4}
\min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})\\
\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d} \geq 1\times\sum_{v=1}^{V} \forall s, \\
 &\textstyle  \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d,, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
\end{alignat}
\end{subequations}
\textbf{RL model}

Here, we need to know agents, states, actions and rewards.
\begin{itemize}
    \item \textbf{Agents} are the services that have slices and each slice have set of VNFs.
    \item \textbf{States}: We have $2^{D_c}$ states that whether each data center is on or off.
    \item \textbf{Actions}: Each action can be defined by connecting set of VNFs of one slice to a DC.
    \item \textbf{Rewards}: the rewards is to minimize the number of using data centers. (minimize power of data centers)
\end{itemize}
%%%
In addition, in each time the deploying a new VNF on a VM needs more power.
\begin{equation*}
\textstyle \phi_{diff} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}[y_{s,d}(t)-y_{s,d}(t-1)]^+\phi_{s,d}^{new}.
\end{equation*}
%%
Also, a cost function for the placement of VNFs into DCs is defined as
\begin{equation}\label{eqpsi}
\textstyle  \psi_{tot} = \phi_{tot} + \phi_{diff}
\end{equation}
where, $\nu$ is a design variable to value between the first term of \eqref{eqpsi} which is the total power consumption of physical resources and the second term that is shown the amount of admitted slices to have physical resources.
\begin{subequations}
\begin{alignat}{4}
\min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})\\
\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}(t) \geq 1 \forall s, \\
 &\textstyle  \sum_{s=1}^{S} y_{s,d}(t) \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d,, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
\end{alignat}
\end{subequations}
\item \textbf{Network Slicing}

Suppose there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $ consists of $U_v$
single-antenna UEs that require certain service. Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RUs and $K_s$ physical resource blocks (PRBs), one DU and one CU that contains VNFs.
Slices can have shared resources. All RUs in a slice, that are mapped to a service, transmit signals cooperatively to all the UEs in a specific service. Each RU $r \in \{1,2,...,R \}$ is mapped to a DU via an optical fiber link with limited fronthaul capacity.
There are two processing layers one in the DU and one in the CU of ORAN system, each represented with a VNF. The lower layer (i.e., DU) consists of high-PHY, MAC, and RLC, and the upper layer (i.e., CU) consists of RRC, PDCP and SDAP. Assume we have $M_1$ VNFs in the DU layer and $M_2$ VNFs in the CU layer for processing data.
Each VNF in both layers belongs to one or more slices. So, in the $s^{th}$ slice, there are $M_{s,1}$ VNFs in the DU layer and $M_{s,2}$ VNFs in the CU layer. The VNFs in the DU and CU layers have the computational capacity that is  equal to $\mu_1$ and $\mu_2$, respectively.
Also, RUs and PRBs can serve more than one slice.
\subsection{The Achievable Rate}
The achievable data rate for the $i^{th}$ UE in the $v^{th}$ service can be written as
\begin{equation}\label{eq1}
\mathcal{R}_{u(v,i)} = B \log_2({1+ \rho_{u(v,i)}}),
\end{equation}
where $B$ is the bandwidth of system and $\rho_{u(v,i)}$ is the SNR of $i^{th}$ UE in $v^{th}$ service which is obtained from
\begin{equation}\label{eq2}
\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H |^2 a_{v,s}}{BN_0 + I_{u(v,i)}},
\end{equation}
where, $a_{v,s}$ is a binary variable denotes whether the slice $s$ is mapped to service $v$ or not .

\subsection{Mean Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(v,i)}$ for the $i^{th}$ UE of the $v^{th}$ service.
Therefore, the mean arrival data rate of UEs mapped to the $s^{th}$ slice in the CU layer is $\alpha_{s_1} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}\lambda_{u(v,i)}$, where $a_{v,s}$ is a binary variable which indicates whether the $v^{th}$ service is mapped to the $s^{th}$ slice or not.
Furthermore, the mean arrival data rate of the DU layer is approximately equal to the mean arrival data rate of the first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the mean arrival data rate of the second layer which is processed in the first layer is still Poisson with rate $\alpha_{s}$.
It is assumed that there are load balancers in each layer for each slice to divide the incoming traffic to VNFs equally \cite{frdl,luong2018novel,luong2018novel1}.
Suppose the baseband processing of each VNF is depicted as an M/M/1 processing queue.
Each packet is processed by one of the VNFs of a slice. So, the mean delay of the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follow, respectively
\begin{equation}
\begin{split}
d_{s_1} &= \frac{1}{\mu_1 - \alpha_{s}/{M_{s,1}}},\\
d_{s_2} &= \frac{1}{\mu_2 - \alpha_{s}/{M_{s,2}}}.
\end{split}
\end{equation}
where $1/\mu_1$ and $1/\mu_2$ are the mean service time of the first and the second layers respectively.
Besides, $\alpha_{s}$ is the  arrival rate which is divided
by load balancer before arriving to the VNFs. The  arrival rate of each VNF in each layer of the slice $s$ is $\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$.
In addition, $d_{s_{tr}}$ is the transmission delay for $s^{th}$ slice on the  wireless link. The arrival data rate of wireless link
 is equal to the arrival data rate of load balancers for each slice \cite{frdl}.
Moreover, it is assumed that the service time of transmission queue for each slice $s$ has
 an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. Therefore,
the mean delay of the transmission layer is
\begin{equation}
 d_{s_{tr}} = \frac{1}{R_{{tot}_s} - \alpha_{s}};
\end{equation}
where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}R_{u(v,i)}$ is the total achievable rate of each slice that is mapped to specific service.
Mean delay of each slice is obtained as below.
\begin{equation}
D_{s} = d_{s_1} + d_{s_2} + d_{s_{tr}} \forall s.
\end{equation}
An important criterion to measure the optimality of a system is energy efficiency represented as the sum-rate to sum-power
\begin{equation}
\textstyle \eta(\boldsymbol{P},\boldsymbol{A}) := \frac{\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} }{\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}} = \frac{\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A})}{P_r^{{tot}}(\boldsymbol{P},\boldsymbol{A})},
\end{equation}
where, $P_r^{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$ is the total power consumption of all RUs in all slices. Also, $\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $ is the total rates of all UEs applied for all types of services.
The main problem is
\begin{subequations}
\begin{alignat}{4}
\max\limits_{\boldsymbol{P}, \boldsymbol{A} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})\\
\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i,   \\
&p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k, \\
&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} && \quad \forall v, \forall k, \\
&D_{s} \leq D_{s}^{max}  &&\quad \forall s, \label{cc15} \\
& \textstyle  \sum_{s=1}^{S}a_{v,s} \geq 1 &&\quad \forall s.
\end{alignat}
\label{constraints1}
\end{subequations}
\textbf{RL model}

Here, we need to know agents, states, actions and rewards.
\begin{itemize}
    \item \textbf{Agents}: are the services 
    \item \textbf{States}: set of $A$ and $P$
    \item \textbf{Actions}: Whether service i map to slice j and choose which power.
    \item \textbf{Rewards}: the rewards is to maximize energy efficiency subject to constraints.
\end{itemize}

\end{enumerate}
\bibliographystyle{IEEEtran}
\bibliography{references}
\end{document}
